A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-01 mt-marathon.2013/PBML_article.tex
start adding bibs

\end{algorithmic}
\caption{Comparing Hypothesis States (old framework}
\label{algo:CompareHypoStates}
\end{figure}

\subsection{New Framework}        
 All feature functions inherit indirectly from the class

    FeatureFunction

which provides basic services to all feature functions such as storing the name and number of dense features, and providing a central repository of all feature functions.

A feature function can be stateless or stateful, depending on whether it inherits from

StatelessFeatureFunction

StatefulFeatureFunction

The state comparison routine of Figure (1) evolved to a more general comparison of states from all stateful feature functions, Figure (2).

    CompareHypotheses(a, b)

       if Coverage(a) != Coverage(b)

         return not equal

        for each feature function state s

          if (state type s for hypothesis a) != (state type s for hypothesis b)

             return not equal

        end-for
        return equal

\subsection{CDEC and Joshua}
CDEC and Joshua both have modern feature function frameworks similar to the Moses new framework. CDEC has no distinction between stateful and stateless features; stateless features have zero size states.

\section{Scoring}
\subsection{Old Framework}
The types of feature functions were hardcoded when evaluating the scores of translation rules and hypotheses. For example, a translation rule is scored according to Equation (1)

>>>>

\end{algorithmic}
\caption{Comparing Hypothesis States (old framework)}
\label{algo:CompareHypoStates}
\end{figure}

\subsection{New Framework}        
 All feature functions inherit indirectly from the class \emph{FeatureFunction}, which provides basic services to all feature functions such as storing the name and number of dense features, and providing a central repository of all feature functions.

A feature function can be stateless or stateful, depending on whether it inherits from \emph{StatelessFeatureFunction} or \emph{StatefulFeatureFunction}, respectively.

The state comparison routine of Figure~\ref{algo:CompareHypoStates} evolved to compare the state of all stateful feature functions, Figure~\ref{algo:CompareHypoStates.new}.

        \FORALL {feature function state s}
          \IF {state s of hypothesis a != state s for hypothesis b}
	    \RETURN not equal
	 \ENDIF
        \ENDFOR
        \RETURN equal

\end{algorithmic}
\caption{Comparing Hypothesis States (new framework)}
\label{algo:CompareHypoStates.new}
\end{figure}

\subsection{cdec and Joshua}
cdec and Joshua both have modern feature function frameworks similar to the Moses new framework. cdec has no distinction between stateful and stateless features; stateless features have zero size states.

\section{Hypothesis Evaluation}
\subsection{Old Framework}
The types of feature functions were hardcoded when evaluating the scores of translation rules and hypotheses. For example, a translation rule is scored according to Equation (1)
